Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$

### 2015-01-30 doc/HH4b_Documentation.tex
Updated docs

The NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples. At the generator level the following basic cuts are applied. Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$. Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$. Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Process & Filename & Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
\hline
\hline
$pp \to HH$ & HH\_sm\_eft\_100K.lhe & MG5\_aMC@NLO & 100K & $1.729\times10^{-2}$ pb \\
\hline
$pp \to b\bar{b}b\bar{b}$ & SHERPA\_QCD\_4b.hepmc & SHERPA 2.1.1 & 3M &$1.016 \times10^3$ pb \\
$pp \to b\bar{b}jj$ & SHERPA\_QCD\_2b2j.hepmc & SHERPA 2.1.1 & 3M & $4.076 \times 10^5$ pb\\
$pp \to jjjj$ & Running & SHERPA 2.1.1 & 3M  & ??? \\
$pp \to t\bar{t}$ &  & &  & \\
\hline
\end{tabular}
\caption{Summary of generated samples to date} \label{tab:samples}
\end{center}
\end{table}%

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Process & $\sigma$ aMC@NLO & $\sigma$ Oxford (SHERPA) \\
\hline\hline
$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $3.473\times10^{-1}$ pb \\ 
$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$5.193 \times 10^2$ pb \\ 
\hline
\end{tabular}
\caption{Comparison of LO Oxford SHERPA cross-sections with those of the aMC@NLO paper. The aMC@NLO cross-sections come with a quoted $~50\%$ theory uncertainty.} \label{tab:xsecs}
\end{center}
\end{table}%
\section{Object and Event Selection}

@@

\subsubsection{Resolved $b$-jet tagging efficiencies}
In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$. In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_b\epsilon^2_l$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ & After b-tag & \% selected & \% Naive selection \\
\hline \hline
$H\bar{H}$ & $1.729 \times 10^{-2}$ pb & $1.565\times 10^{-3}$ pb & \textbf{9.050\%} & 40.96\% \\
\hline
$b\bar{b}b\bar{b}$ & $1.016 \times10^3$ pb & $93.46$ pb & \textbf{9.199\%} & 40.96\%\\
$b\bar{b}jj$ &  $4.076 \times 10^5$ pb & 103.904 pb & \textbf{0.026\%} & 0.0064\% \\
\hline
\textbf{S/B} & $4.23 \times 10^{-8}$ & $7.93 \times 10^{-6}$& \multicolumn{2}{c}{}\\
\cline{1-3}
\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $4.68 \times 10^{-2}$ & $1.93 \times 10^{-1}$& \multicolumn{2}{c}{}\\
\cline{1-3}
\end{tabular}
\end{center}
\caption{$b$-tagging analysis performed upon the samples described in Section~\ref{sec:samples}. Cross-sections are given for the samples before and after the application of the b-tagging procedure whereby the four hardest jets in the event are used, and the flat selection efficiency and mis-tag rates applied. The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison. Finally, the signal-to-background ratio and significance are given both before and after the b-tagging, for $\mathcal{L}=$ 3 ab$^{-1}$.} \label{tab:btageff1}
\end{table}%

@@

\begin{table}[htdp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c||c|}
\hline
Process & 0 $b$-jets & 1 $b$-jet & 2 $b$-jets & 3 $b$-jets & 4 $b$-jets & \% selected \\
\hline\hline
$H\bar{H}$ & 0.049\% &  2.448\% &  23.49\% & 52.58\% &  21.43\% & \textbf{9.050\%}\\
\hline
$b\bar{b}b\bar{b}$ & 0.429\% & 5.477\%   & 25.53\% & 46.67\%  &  21.89\% & \textbf{9.208\%} \\
$b\bar{b}jj$ & 6.213\%  &40.56\%  &51.93\%  &  1.227\% & 0.072\% & \textbf{0.039\%}\\
\hline
\end{tabular}
\end{center}
\caption{Breakdown of the number of true $b$-jets in the hardest four clustered jets for various samples. The final column shows the predicted pass rate for the $b$-tagging given the distribution of events in the preceding columns.}\label{tab:nbjets}
\end{table}%

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & \% selected  \\
\hline \hline
$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & 7.467\% \\
\hline
$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & 5.472\% \\
$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & 0.0224\% \\
\hline
\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& \multicolumn{1}{c}{}\\
\cline{1-3}
\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& \multicolumn{1}{c}{}\\
\cline{1-3}
\end{tabular}
\end{center}
\caption{Summary of the $b$-tagging procedure of the UCL analysis. Presented as in Table~\ref{tab:btageff1}. In this case the total cross-sections are presented after a cut requiring four anti-$k_T$ R=0.5 jets with $p_T>40$ GeV in the final state. The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison.}\label{tab:UCLbtag}
\end{table}%

@@

@@

}(processes);
(selector){
  PT 5 20 7000
  PT -5 20 7000
  PseudoRapidity 5 -3.0 3.0
  PseudoRapidity -5 -3.0 3.0
}(selector);
\end{verbatim}

@@

}(processes);
(selector){
  PT 5 20 7000
  PT -5 20 7000
  PseudoRapidity 5 -3 3
  PseudoRapidity 5 -3 3

  PT 93 20 7000
  PseudoRapidity 93 -3 3
}(selector);
\end{verbatim}

@@

>>>>

The NNPDF 3.0 $n_f = 4$ LO set with strong coupling $\alpha_S=0.118$ is used for all samples. At the generator level the following basic cuts are applied. Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located within $| \eta | \le 3.0$. All final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$. Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$. Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{tot}}$ \\
\hline
\hline
$pp \to HH$ &  MG5\_aMC@NLO & 100K & $1.729\times10^{-2}$ pb \\
\hline
$pp \to b\bar{b}b\bar{b}$ &  SHERPA 2.1.1 & 3M &$9.298 \times10^2$ pb \\
$pp \to b\bar{b}jj$ &  SHERPA 2.1.1 & 3M & $2.208 \times 10^5$ pb\\
$pp \to jjjj$ &  SHERPA 2.1.1 & 3M  & $9.709\times 10^6$ pb \\
$pp \to t\bar{t}$ (had) &  SHERPA 2.1.1 & 100K & $2.511\times 10^3$ pb \\
\hline
\end{tabular}
\caption{Summary of generated samples to date} \label{tab:samples}
\end{center}
\end{table}%

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Process & $\sigma$ aMC@NLO & $\sigma$ Oxford (SHERPA) \\
\hline\hline
$b\bar{b}b\bar{b}$ & $5.050 \times  10^{-1}$ pb & $3.492\times10^{-1}$ pb \\ 
$b\bar{b}jj$ & $1.852 \times 10^2$ pb &$4.209 \times 10^2$ pb \\ 
$jjjj$ & -  & $4.450\times 10^4$ pb \\
\hline
\end{tabular}
\caption{Comparison of LO Oxford SHERPA cross-sections with those of the aMC@NLO paper. The aMC@NLO cross-sections come with a quoted $~50\%$ theory uncertainty.} \label{tab:xsecs}
\end{center}
\end{table}%
\section{Object and Event Selection}

@@

\subsubsection{Resolved $b$-jet tagging efficiencies} \label{sec:btagtest}
In order to perform an initial validation of the $b$-tagging procedure used in our resolved analysis we consider first a simple flat $b$-jet tagging efficiency of $\epsilon_b=0.8$ and a light jet mis-tag rate of $\epsilon_l=0.01$. In the UCL diHiggs analysis~\cite{Wardrope:2014kya} the 2$b$2$j$ background was discarded by applying a naive selection factor of $\epsilon^2_b\epsilon^2_l$ to a similar $2b2j$ cross-section as in Table~\ref{tab:xsecs} and finding the resulting cross-section to be considerably smaller than the equivalent selection factor applied to the 4$b$ sample.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ & After b-tag & \% selected & \% Naive selection \\
\hline \hline
$H\bar{H}$ & $1.729 \times 10^{-2}$ pb & $1.460\times 10^{-3}$ pb & \textbf{8.444\%} & 40.96\% \\
\hline
$b\bar{b}b\bar{b}$ & $9.298 \times10^2$ pb & $78.32$ pb & \textbf{8.423\%} & 40.96\%\\
$b\bar{b}jj$ &  $2.208 \times 10^5$ pb & $84.80$ pb & \textbf{0.038\%} & 0.0064\% \\
$jjjj$ & $9.709\times 10^6$ pb & $20.85$ pb & \textbf{2.147 $\times$ 10$^{-4}$\%} & $1.0\times 10^{-6}$\%\\
\hline
\textbf{S/B} & $1.74 \times 10^{-9}$ & $7.94 \times 10^{-6}$& \multicolumn{2}{c}{}\\
\cline{1-3}
\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $9.50 \times 10^{-3}$ & $1.86 \times 10^{-1}$& \multicolumn{2}{c}{}\\
\cline{1-3}
\end{tabular}
\end{center}
\caption{$b$-tagging analysis performed upon the samples described in Section~\ref{sec:samples}. Cross-sections are given for the samples before and after the application of the b-tagging procedure whereby the four hardest jets in the event are used, and the flat selection efficiency and mis-tag rates applied. The percentage of cross-section surviving the selection is shown, along with the naive expectation ($\epsilon_b^{n_b}\epsilon_l^{n_l}$) for comparison. Finally, the signal-to-background ratio and significance are given both before and after the b-tagging, for $\mathcal{L}=$ 3 ab$^{-1}$.} \label{tab:btageff1}
\end{table}%

@@

\begin{table}[htdp]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c||c|}
\hline
Process & 0 $b$-jets & 1 $b$-jet & 2 $b$-jets & 3 $b$-jets & 4 $b$-jets & \% selected \\
\hline\hline
$H\bar{H}$ & 0.083\% & 2.599\% &  24.712\% &   52.651\% &  19.955\% & \textbf{8.445\%}\\
\hline
$b\bar{b}b\bar{b}$ & 0.858\% &  7.606\% &  27.523\% &  43.977\% &   20.036\% & \textbf{8.434\%} \\
$b\bar{b}jj$ & 9.115\% &    41.792\% &    47.806\% &     1.216\% &  0.071\% & \textbf{0.038\%}\\
$jjjj$ & 95.668\% &   3.789\% &  0.531\% & 0.011\%  & 3.00E-4\%& \textbf{2.17$\times 10^{-4}$\%}\\
\hline
\end{tabular}
\end{center}
\caption{Breakdown of the number of true $b$-jets in the hardest four clustered jets for various samples. The final column shows the predicted pass rate for the $b$-tagging given the distribution of events in the preceding columns.}\label{tab:nbjets}
\end{table}%

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
Process & $\sigma_{\mathrm{tot}}$ (4 Jets $p_T>40$ GeV) & After b-tag & \% selected  \\
\hline \hline
$H\bar{H}$ & $1.081 \times 10^{-2}$ pb & $8.1147\times 10^{-4}$ pb & 7.467\% \\
\hline
$b\bar{b}b\bar{b}$ & $7.239 \times10^1$ pb & $3.961$ pb & 5.472\% \\
$b\bar{b}jj$ &  $2.137 \times 10^4$ pb & 4.779 pb & 0.0224\% \\
\hline
\textbf{S/B} & $5.04 \times 10^{-7}$ & $9.28 \times 10^{-5}$& \multicolumn{1}{c}{}\\
\cline{1-3}
\textbf{S/$\sqrt{\mathrm{\textbf{B}}}$}& $1.27 \times 10^{-1}$ & $4.75 \times 10^{-1}$& \multicolumn{1}{c}{}\\
\cline{1-3}
\end{tabular}
\end{center}
\caption{Summary of the $b$-tagging procedure of the UCL analysis. Presented as in Table~\ref{tab:btageff1}. In this case the total cross-sections are presented after a cut requiring four anti-$k_T$ R=0.5 jets with $p_T>40$ GeV in the final state. The percentage selected column is given for the $b$-tagging stage \emph{only} for comparison. \textbf{Needs to be updated to newer samples}.}\label{tab:UCLbtag}
\end{table}%

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\textwidth]{plots/m4b_ucl_preCut.pdf}
\caption{Contributions from the various samples to the observed four $b$ invariant mass system after applying the $b$-tagging procedure outlined in Section~\ref{sec:btagtest}.}
\end{center}
\end{figure}

@@

}(processes);
(selector){
  PT 5 20 7000
  PT -5 20 7000
  PseudoRapidity 5 -3.0 3.0
  PseudoRapidity -5 -3.0 3.0

  DeltaR 5 5 0.1 10000
  DeltaR 5 -5 0.1 10000
  DeltaR -5 -5 0.1 10000
}(selector);
\end{verbatim}

@@

}(processes);
(selector){
  PT 5 20 7000
  PT -5 20 7000
  PseudoRapidity 5 -3 3
  PseudoRapidity -5 -3 3

  PT 93 20 7000
  PseudoRapidity 93 -3 3

  DeltaR 93 93 0.1 10000
  DeltaR 5 93 0.1 10000
  DeltaR -5 93 0.1 10000
  DeltaR 5 5 0.1 10000
  DeltaR -5 5 0.1 10000
  DeltaR -5 -5 0.1 10000
}(selector);
\end{verbatim}

@@

\subsection {Background: QCD ttbar}
\begin{verbatim}
(run){
  EVENTS 3M;
  EVENT_GENERATION_MODE U;
  ME_SIGNAL_GENERATOR Comix;

  EVENT_OUTPUT HepMC_Short[SHERPA_QCD_ttbar];

  SCF:=1; ### default scale factor
  SCALES VAR{SCF*H_T2/4};

  # Stable mode 0 specified that both particle and antiparticle are unstable
  STABLE[6] = 0;
  STABLE[24] = 0;

  # Enable only fully hadronic decay modes
  HARD_DECAYS=1;   
  HDH_NO_DECAY={24,12,-11}|{24,14,-13}|{24,16,-15}|{-24,-12,11}|{-24,-14,13}|{-24,-16,15};

}(run);

(processes){
  Process 93 93 -> 6 -6;
  Order_EW 0;
  End process;
}(processes);

(selector){
  PT 6 20 7000
  PT -6 20 7000
  PseudoRapidity 6 -3 3
  PseudoRapidity -6 -3 3
  DeltaR 6 -6 0.1 10000
}(selector);
\end{verbatim}

\clearpage
\section{Decay tables for $t\bar{t}$}

\begin{verbatim}
Decay table for : W+.
Total width:                  2.10561 GeV
Flavour width:                2.06 GeV
----------------------------------------
{24,2,-1}         W+ --> u db              0.702203   GeV, BR= 33.3492 %
{24,4,-3}         W+ --> c sb              0.701546   GeV, BR= 33.318 %
{24,12,-11}       W+ --> nu_e e+           0.234068   GeV, BR= 11.1164 %
{24,14,-13}       W+ --> nu_mu mu+         0.234066   GeV, BR= 11.1163 %
{24,16,-15}       W+ --> nu_tau tau+       0.233725   GeV, BR= 11.1001 %
----------------------------------------

Decay table for : W-.
Total width:                  2.10561 GeV
Flavour width:                2.06 GeV
----------------------------------------
{-24,-2,1}        W- --> ub d              0.702203   GeV, BR= 33.3492 %
{-24,-4,3}        W- --> cb s              0.701546   GeV, BR= 33.318 %
{-24,-12,11}      W- --> nu_eb e-          0.234068   GeV, BR= 11.1164 %
{-24,-14,13}      W- --> nu_mub mu-        0.234066   GeV, BR= 11.1163 %
{-24,-16,15}      W- --> nu_taub tau-      0.233725   GeV, BR= 11.1001 %
----------------------------------------

Decay table for : t.
Total width:                  1.59689 GeV
Flavour width:                1.5 GeV
----------------------------------------
{6,24,5}          t --> W+ b               1.59689    GeV, BR= 100   %
----------------------------------------

Decay table for : tb.
Total width:                  1.59689 GeV
Flavour width:                1.5 GeV
----------------------------------------
{-6,-24,-5}       tb --> W- bb             1.59689    GeV, BR= 100   %

\end{verbatim}
